\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-04-28 latex_reviewcomments/ReviewCommentsResponse.tex

\question 18. p. 10, lines 246-248.  Please consider replacing “are screened” with “were screened” and removing the hyphen after plug. 
\begin{solution}
Correction made.
\end{solution}

\question 19. p. 10, section 3.3.  Either the text (lines 245-252) or the caption for Figure 8 should say a bit more (a sentence would be adequate) about the clustering process.  For example, the caption could note that the rows for each month refer to days of the week (if this is true) and could name (describe) each of the clusters (i.e., clusters that nominally align with weekdays, Saturdays and Sundays/school holidays). 
\begin{solution}
The caption for Figure 8 was revised significantly to describe what the reader is seeing in the typical average profiles on the left and the days corresponding with
each cluster on the right. Text was added in the preceding paragraphs that briefly describe the significance of each of the clusters.
\end{solution}

\question 20. p. 10., lines 253-259.  Please rewrite the sentence to avoid “compared … to create… scenario for comparison.” What is meant by “measurements were deemed most accurate during the appropriate seasons?”
\begin{solution}
The first sentence of that paragraph was rewritten to avoid the use of "comared" and "create a scenario for comparison". The sentence pertaining to the seasonal nature of the data analysis was removed as it didn't add any information to the fact that only heating and cooling seasonal data was used for each calibration.
\end{solution}

\question 21. p. 11, lines 261-262.  The NMBE for heating and cooling are exactly the same and the NMBE for cooling is not in accord with the bar charts in Figure 9. 
\begin{solution}
\end{solution}

\question 22. p. 11, section 3.4.  Please see the following comments for the two associated figures.  In addition, the presentation of results from the study of Miller et al. is not clear.  Does the Miller study compare solo and co-simulation results?  If so, which results are the reference for the percentage changes? Should the reader conclude that the differences between Miller and this study are comparable (which is comforting) or that deviations are significant, in which case they should be explained. 
\begin{solution}
\textcolor{red}{Confirm in the Juypter notebook}
\end{solution}

\question 24. p. 12, Figure 11.  The text states Figure 11 shows differences in predicted heating consumption and notes there is a consistent offset across days in January.  Figure 11 shows hourly variations for presumably averaged days and single points for each month; in short, variations across days cannot be discerned.  Are these variations important to the comparison?  The order of the bars matches Figure 10 but disagrees with Figure 9.  The text compares co-simulation with measurement (using the latter as the reference, which seems appropriate) and shows 2\% annual difference but the numbers over the bars appear to compare co-simulation and measurement with solo simulation and show 6.5\% difference.  As in Figure 11, the numbers (not percentages) over the bars are not explained. 
\begin{solution}
\textcolor{red}{Update graphics}
\end{solution}

\question 25. p. 12, section 3.5.  The text should include a reference to the Minergie standard and the caption or image in Figure 12 should identify the STCC building. 
\begin{solution}
\textcolor{red}{Add Minergie as a reference}
\end{solution}

\question 
26. p. 13, line 308.  Please explain SIA and/or provide an appropriate reference.   
\begin{solution}
\textcolor{red}{Add SIA and explain}
\end{solution}

\question 
27. p. 13, lines 310-313.  The text states that the CItySIm model was created from a DXF file from EnergyPlus.  Was this export used solely for the STCC building or was the remainder of the Quartier Nord as shown in Figure 13 designed in Open Studio? 
\begin{solution}
\textcolor{red}{Jerome -- any feedback on this?}
\end{solution}

\question 
28. P. 13, lines 316-322.  The reference in the text for percentage changes is the EnergyPlus simulation but Figures 14 and 15 place the percentages (with opposite sign) about the solo simulations.  The text states that discrepancies between solo and co-simulations are due to differences in calculation of heating and cooling loads.  Please elaborate. 
\begin{solution}
\textcolor{red}{Confirm numbers in graphics}
\end{solution}

\question 
29. P. 14, section 3.8.  The text states that the Quartier Nord building was also simulated. This is a bit confusing because Quartier Nord previously referred to the complex.  Does the building refer to the building on the right in Figures 12 and 13 – i.e., everything except the STCC?  The text also states that differences between solo and co-simulations are small because the surroundings are sparse.  If this is the case, would one expect better agreement between solo and co-simulations for the neighboring STCC?  Also, please consider replacing “due to” with “because” in line 327. 
\begin{solution}
\textcolor{red}{Jerome -- can you clarify this?}
\end{solution}

\question 
30. p. 15.  Conclusion.  There is no summary of strengths and weakness of the process presented in the paper and the future work is limited only to more practical implementation.  Is there nothing to improve? 
\begin{solution}
\textcolor{red}{Update with strengths and weaknesses in the discussion}
\end{solution}

\question 
31. p. 16. The first and last references, by Miller et al. and Zhang et al., lack volume and page numbers.  Throughout the reference section, the authors should consider consistency in use of initials versus given names.   
\begin{solution}
\textcolor{red}{Update references}
\end{solution}

@@

\subsection{Revision items}

\question 
(1) At the top of page 2, the paper describes advantages of EnergyPlus. However, it is not clear why this simulation engine is used when several others could perform the presented analyses. It is important to know what technical aspects of the co-simulation procedure specifically drove the authors to use EnergyPlus. 
\begin{solution}
\textcolor{red}{Update references}

\end{solution}

\question 
(2) The actual co-simulation, which is the main contribution of this study is not well discussed. Specifically, the paper needs to describe: (a) frequency of data exchanges, (b) whether any data averaging took place, (c) whether the numerical scheme is stable and grid independent, (d) what is the time step for each engine?, (e) what is the simulation time?, (f) are these annual, monthly, or daily simulations?, (g) what convergence criterion was used? 
\begin{solution}
\textcolor{red}{Daren -- can you take a stab at these?}
a) \\
b) \\
c) \\
d) \\
e) \\
f) \\
g) \\
\end{solution}

\question 
(3) Figure 3, Section 2.3, and Figure 4 are the same or similar to author’s previous publication. A citation would be sufficient. 
\begin{solution}
We chose to replicate these figures in this publication to clarify the bigger picture of the scope of the study. We believe these figures help to put the current study in context in a better way.
\end{solution}

\question 
(4) In Section 3.3, the paper needs many more details on the calibration process, including the specification of all calibration steps undertaken, rather than just cursory listing some of the steps. 
\begin{solution}
\textcolor{red}{Explain the calibration process in much more detail}
\end{solution}

\question 
(5) Please, discuss results in Figure 10. What are the numerical or physical reasons for the “solo” case to underperform? 
\begin{solution}
\textcolor{red}{Why are there differences?}

@@

\end{solution}

\question 
(6) The conclusions need content on co-simulation execution challenges and how they were overcome during the course of that this study.
\begin{solution}
\textcolor{red}{Strenghts and weaknesses and advantages/disadvantages in the}

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
addresses review one, item k) part one (Figure 2)

\begin{abstract}
    This paper describes the co-simulation process of the building and urban
    scale models of two campuses of higher education buildings in Switzerland.
    The campuses are modeled at both the building level, using the EnergyPlus
    simulation engine, and at the urban scale using the CitySim engine. A co-
    simulation framework is used to execute simulations from both engines
    concurrently with an exchange of information to leverage the various
    strengths of each. In the first case study, on-site weather and measured
    performance data are then compared to the output from two modeling
    scenarios: building-scale simulation using EnergyPlus and co-simulation of
    the engines. A partial calibration process is implemented to reconcile the
    simulations with the measured data of a targeted office building on
    campus. In the second case study, the co-simulation results are compared
    to the both the CitySim simulation and EnergyPlus engines. The results
    show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
    -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
    heating consumption as compared to solo simulations. Challenges encountered with the urban scale
    calibration and the strengths and weaknesses of the developed process are
    discussed.
\end{abstract}

@@

\section{Introduction}
% \noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}

Urban scale building performance simulation is a process that empowers the
analysis and optimization of cities. Urban populations are growing around the
world at an unprecedented rate. A transition from urban to rural is underway and
2.5 billion people are expected to join cities throughout the world
\citep{UnitedNations:2014vn}. Expansions of entire districts and even cities
is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
modeling is in the midst of an intense focus on the research community with
six key areas of practice: technology design, building design, urban climate,
systems design, policy assessment, and land use and transportation
\citep{Keirstead:2012ct}. The ability to simulate the interaction between
large collections of buildings enables the development and testing of
optimization and planning scenarios for this new development
\citep{Dorer:2013vt}.

The CitySim simulation engine is an example of such a program designed and
optimized for urban-scale simulation. CitySim is an urban performance
simulation engine that comprises a Solver module as well as a graphical user
interface. It focuses on the energy flows of multiple simplified building
models and their interdependent relationship with their urban climate
\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
occupant behavior, and plant/equipment models integrated as a single
simulation engine. CitySim simulates multiple buildings up to city scale using
simplified models to achieve a good compromise between modeling
accuracy, computational overheads, and data availability. Each building's
thermal behavior is based on an electrical analogy using a two node resistor-
capacitor network. The internal lighting, people, and miscellaneous loads are
modeled using a simplified occupancy-based approximation. The heating,
ventilation, and air-conditioning (HVAC) systems are modeled using a single
equation that approximates the total mass flow rate required to meet the
sensible and latent loads of each building as a whole. Each of these
simplifying approximations empowers the urban-scale simulation to have
reasonable execution times on the number of buildings being
simulated.

@@

Both building and urban-scale simulation domains have rightfully chosen
boundary conditions that reflect their key goals while seeking to minimize the
input parameters necessary and run-times of the engines themselves. This focus
results in certain deficiencies concerning modeling various phenomenon.
For example, urban scale simulation highly simplifies the building systems and
internal load models, thus making a retrofit analysis at the systems level
difficult. And whole building simulation in EnergyPlus neglects many of the
various contextual consideration of the urban environment such as long wave
radiation exchange with adjacent surfaces and localized urban weather effects
\citep{Lawrie:2001vf}.%\noteDT{ref?}

To address the deficiencies of the individual engines, the current
effort seeks to couple building and urban scale simulation. The research in
this paper is part of a larger coupling effort in which various engines are
connected and co-simulated to create a more comprehensive analysis of the
urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target is the
computational interface between the building energy model, using EnergyPlus,
and the urban energy model using CitySim. An overview of the larger scope is
shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as the interface between the City Energy Simulation (CES) model and the
Building Energy Simulation (BES) model.

@@

This paper describes the achievement of several objectives:
\begin{enumerate}
  \item Automation of the process of simultaneous meta-data extraction from a
  building information model (BIM) for the creation of both building and
  urban-scale performance models for a real-world campus of buildings
  \item Co-simulate the urban and building scale models through concurrent information exchange
  \item Implement a simplified calibration procedure based on reconciling the
  co-simulation output results for a target building using measured energy
  performance data from the campus energy information system (EIS)
\end{enumerate}

@@

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is done at the subsystem and building-scale. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{Zhang:2013vx} and to improve energy prediction
\citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{Yang:2012cr}. It was also coupled with simplified lumped parameter
models to facilitate comparison with measured sensor data
\citep{Martin:2015fj}. EnergyPlus and the TEP Urban Canopy Model program were
coupled to quantify the influences of urban localized weather effects
on whole building simulation \citep{Bueno:2011hi} and urban weather generation
\citep{Bueno:2013hh}.
% Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
% \subsection{Urban scale performance simulation}

@@

\subsection{Coupling process} 
The coupling process of a simplified single zone
model and contextual surrounding buildings is described in previous studies
\citep{thomas2014multiscale}, which forms the basis for the methodology
in the current effort. This process utilizes the Design Performance Viewer
(DPV) and associated workflow. The DPV is a tool written to extract and
simulate an EnergyPlus input data file (IDF) from an
Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
\citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
of the building information model from the earliest design possible and can be
used throughout the life-cycle of the building including retrofit analysis
\citep{Miller:2014tu}. This process is achieved by augmenting the information
in the BIM with default values and abstracting information not relevant for
energy simulation. The tool already has a simplified notion of surrounding
buildings, which are modeled in the BIM as simple mass objects without further
information and are exported as shading surfaces to EnergyPlus. This
functionality is used for creating the CitySim mass scene and leads to a crude
model of the urban context of the building. The current DPV philosophy of
allowing the designer to iterate rapidly on early design decisions based on
feedback about the performance of the design remains. This approach includes
streamlining the process where running a simulation requires no effort from
the designer due to automatic creation of input files, execution, and analysis
of the results.% \noteDT{not sure the second reference includes coupling...}

The coupling process of EnergyPlus and CitySim is shown in Figure
\ref{fig:OverallWorkflowProcess}. First, the DPV is used to extract an
EnergyPlus simulation model from the BIM. The DPV utilizes the Revit API to
extract geometrical information about the building and the physical properties
of walls, windows, doors, roofs, and floors. This information is encoded in the
BIM model as wall types, roof types, floor types as well as window and door
families. Wherever possible, the tool uses the layering and materials of the
construction types, enhancing them with physical attributes relevant to
EnergyPlus. Where not defined, it assumes default values.

@@

% On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps. 
Several key urban-scale weather variables are sent to EnergyPlus from CitySim
to account better for the localized effects of surrounding buildings,
geography and climate conditions. These variables include various outdoor air
conditions such as dry bulb and wet bulb temperatures, dewpoint, humidity, wind
speed and direction, and direct and diffuse solar radiation. These variables
overwrite the input weather variables that EnergyPlus obtains from its weather
file input. CitySim is designed to account for physical phenomenon inherent to
urban environments, that are often neglected in building-scale simulation
environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation
exchange between the simulated building and its surroundings is sent to
EnergyPlus; this process is described in detail in Section \ref{lwradiation}.
Finally, CitySim shares its calculated occupancy schedules as it uses a more
robust model of occupants behavior
\citep{Haldi:2011dr}.

@@

Variables sent to CitySim by EnergyPlus at each time step include several
variables related to the calculation of heating and cooling loads of a
targeted building. These variables are transferred due to the ability of
EnergyPlus to model more detailed building systems, schedules, ventilation and
internal load types than CitySim. For example, EnergyPlus is flexible enough
to model a detailed radiant heating and cooling system that would be
impossible in CiytSim \citep{barbara:2015tz}. EnergyPlus is an engine
optimized to accurately model building-scale systems. Thus, CitySim can take 
advantage of these models through coupling and co-simulation. EnergyPlus sends
the heating and cooling loads, the surface temperatures of the exterior
surfaces and the ventilation flow rates to CitySim.

@@

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed
within a program called VisTrails \citep{Anonymous:Cayf2tu7}. The
implementation of this type of work flow is outlined in previous work focused
on automating DPV using the Kepler platform \citep{Thomas:2012wj}. This
process reduces the effort expended by a designer down to pressing a single
button. This functionality allows an iterative design style informed by
readily available simulation results. An automated work flow to tie the
various steps together and maintain the effortless iterative design process.
VisTrails enables the coupling of various work flow subprocesses script
initializations, executions of the engines, and the compilation of the
outputs. This tool empowers the coupling of various executable files and their
connecting scripts in graphical diagrams that enhances reproducibility and
process automation \citep{Freire:2014tt}. The VisTrails work flow diagram for
the first case study in this paper is seen in Figure \ref{VizTrails}.

@@

\section{Implementation}\label{Implementation and results}
The co-simulation process is implemented on two case studies in Switzerland.
The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland.
The focus of this case study is to compare the impact of the information
exchange through co-simulation within the EnergyPlus engine. The intent on
this campus was to develop techniques for retrofit analysis using EnergyPlus.
The targeted building on this campus is the HPI Building. Raw measured data is
available for many of the buildings on campus, thus a simplified calibration
procedure is used to reconcile the simulation results.\\

The second case study is the EPFL campus in Lausanne, Switzerland. The
targeted building, in this case, was the Quartier Nord complex. The focus of
this study was to compare the output results of both CitySim and EnergyPlus.
Reliable measured data for calibration is not currently available for this
building.

\subsection{Campus case study 1: ETHZ Hoenggerberg Campus}
% {\color{red}This section will describe the ETH Hoenggerberg case study}
%The simulation and calibration process is implemented on a campus case study located in Z\"urich, Switzerland. 
The ETH Z\"urich Hoenggerberg campus includes 32 higher education facilities
 with spaces allocated to laboratories, office space, lecture halls,
 cafeterias, data centers and other types of similar areas. The campus has a
 centralized energy management system (EMS) that contains 807 energy and water
 measurement points from heating, cooling, electricity, city gas, domestic hot
 water, grey water, and general water consumption. %\noteDT{deleted: "buildings"}

@@

% The coupling process outlined is applicable with regards to a targeted building that is surrounded by an adjacent array of buildings. 
% {\color{red}Insert the campus map illustrating the targeted buildings.}

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a
CitySim model of the campus was developed. Through the workflow automation
process, this geometry was converted into an EnergyPlus input file as seen in
Figure \ref{fig:HPIcampus}. The EnergyPlus input file was then used as an input
to execute EnergyPlus solo and co-simulation processes for the purpose of
simplified calibration, and then to understand the magnitude of difference
between these simulation scenarios.% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{figures/HPI_Campus.png}
\caption{The HPI building modeled with OpenStudio for Sketchup}
\label{fig:HPIcampus}
\end{figure}

% \begin{figure}[H]
% \centering
% \includegraphics[scale=0.2]{figures/campuscitysim}
% \caption{Campus modeled in CitySim}
% \label{fig:campuscitysim}
% \end{figure}

\subsection{Measured data collection and calibration}

Energy data from the HPI building was collected and analyzed in the context of
the simplified calibration procedures. The measured datasets are screened and
aggregated into typical usage profiles to be used for the lighting, plug-
loads, and HVAC equipment availability schedules and power densities. Figure
\ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
energy for the HPI building. This profile was created through a filtering and
clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. This
profile is used to set the availability schedules as inputs into the
EnergyPlus simulation to emulate the way occupants inhabit the building and
how the building management system (BMS) controls the lighting and HVAC
systems. 
% This approach is compared to the practice of interviews and site
% visits to determine such input parameters.\noteDT{where??? how??? i don't get
% it...}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/HPI_combinedclusterandcal_5}
\caption{HPI Electrical Energy Typical Profiles}
\label{fig:hpi_elec_profiles}
\end{figure}

>>>>

\begin{abstract}
    This paper describes the co-simulation process of the building and urban
    scale models of two campuses of higher education buildings in Switzerland.
    The campuses are modeled at both the building level, using the EnergyPlus
    simulation engine, and at the urban scale using the CitySim engine. A co-
    simulation framework is used to execute simulations from both engines
    concurrently with an exchange of information to leverage the various
    strengths of each. In the first case study, on-site weather and measured
    performance data are then compared to the output from two modeling
    scenarios: building-scale simulation using EnergyPlus and co-simulation of
    the engines. A partial calibration process is implemented to reconcile the
    simulations with the measured data of a targeted office building on
    campus. In the second case study, the co-simulation results are compared
    to the both the CitySim simulation engine. The results
    show that coupling of EnergyPlus with CitySim resulted in a -15.5\% and
    -7.5\% impact on cooling consumption and a +6.5\% and +4.8\% impact on
    heating consumption as compared to solo simulations of each of the engines. Challenges encountered with the urban scale
    calibration and the strengths and weaknesses of the developed process are
    discussed.
\end{abstract}

@@

\section{Introduction}
\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}

Urban scale building performance simulation is a process that empowers the
analysis and optimization of cities. Urban populations are growing around the
world at an unprecedented rate. A transition from urban to rural is underway and
2.5 billion people are expected to join cities throughout the world by the year 2030
\citep{UnitedNations:2014vn}. Expansions of entire districts and even cities
is not an uncommon phenomenon, especially in East Asia and Africa. Urban scale
modeling is in the midst of an intense focus on the research community with
six key areas of practice: technology design, building design, urban climate,
systems design, policy assessment, and land use and transportation
\citep{Keirstead:2012ct}. The ability to simulate the interaction between
large collections of buildings enables the development and testing of
optimization and planning scenarios for this new development
\citep{Dorer:2013vt}.

The CitySim simulation engine is an example of such a program designed and
optimized for urban-scale simulation. CitySim is an urban performance
simulation engine that comprises a solver module as well as a graphical user
interface. It focuses on the energy flows of multiple simplified building
models and their interdependent relationship with their urban climate
\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
occupant behavior, and plant/equipment models integrated as a single
simulation engine. CitySim simulates multiple buildings up to city scale using
simplified models to achieve a good compromise between modeling
accuracy, computational overheads, and data availability. Each building's
thermal behavior is based on an electrical analogy using a two node resistor-
capacitor network. The internal lighting, people, and miscellaneous loads are
modeled using a simplified occupancy-based approximation. The heating,
ventilation, and air-conditioning (HVAC) systems are modeled using a single
equation that approximates the total mass flow rate required to meet the
sensible and latent loads of each building as a whole. Each of these
simplifying approximations empowers the urban-scale simulation to have
reasonable execution times on the number of buildings being
simulated.

@@

Both building and urban-scale simulation domains have rightfully chosen
boundary conditions that reflect their key goals while seeking to minimize the
input parameters necessary and run-times of the engines themselves. This focus
results in certain deficiencies concerning modeling various phenomena.
For example, urban scale simulation highly simplifies the building systems and
internal load models, thus making a retrofit analysis at the systems level
difficult. And whole building simulation in EnergyPlus neglects many of the
various contextual consideration of the urban environment such as long wave
radiation exchange with adjacent surfaces and localized urban weather effects
\citep{Lawrie:2001vf}.%\noteDT{ref?}

To address the deficiencies of the individual engines, the current
effort seeks to couple building and urban scale simulation. The research in
this paper is part of a larger coupling effort in which various engines are
connected and co-simulated to create a more comprehensive analysis of the
urban scale \citep{Dorer:2013vt,Allegrini:2012kx}. The target is the
computational interface between the building energy model, using EnergyPlus,
and the urban energy model using CitySim. An overview of the larger scope is
shown in Figure \ref{fig:UMEM} and the context of the coupling task appears as 
the interface between the City Energy Simulation (CES) model and the
Building Energy Simulation (BES) model. The scales and models contained in the 
urban environment context include the Urban-Scale Model (UC Model), the UMC model using OpenFoam, 
and the Meteorological Meso-scalce (MM model). On the database side, Revit, global 
information systems (GIS), and building information systems (BIS) are utilized.

@@

This paper describes the achievement of several objectives:
\begin{enumerate}
  \item Automate of the process of simultaneous meta-data extraction from a
  building information model (BIM) for the creation of both building and
  urban-scale performance models for a real-world campus of buildings
  \item Co-simulate the urban and building scale models through concurrent information exchange
  \item Implement a simplified calibration procedure for the first scenario by 
  reconciling the co-simulation output results for a target building using measured energy
  performance data from the campus energy information system (EIS)
\end{enumerate}

@@

\subsection{Previous multi-scale coupling studies}
Previous attempts of information exchange have been implemented between
simulation engines at various scales. Much of the initial co-simulation work
in the literature is done at the subsystem and building-scale. Previous studies
have analyzed strong and loose coupling of engines at this scale
\citep{Trcka:2010cr,Wetter:2011kh}. Coupling of building-scale simulation with
urban-scale computational fluid dynamics (CFD) is attempted for modeling
natural ventilation \citep{Zhang:2013vx} and to improve energy prediction
\citep{Bouyer:2011eha}. A comprehensive review of energy and airflow modeling
of neighborhoods and university campuses was published that includes
strategic aspects of coupling different %\noteDT{did you mean: "strategic"?}b
types of models \citep{Srebric:2015gq}. EnergyPlus has been coupled with ENVI-
met, a micro-climate computational fluid dynamics (CFD) program
\citep{Yang:2012cr}. It was also coupled with simplified lumped parameter
models to facilitate comparison with measured sensor data
\citep{Martin:2015fj}. While not directly coupled, EnergyPlus and the TEP Urban Canopy Model program were connected
through a modified weather file to quantify the influences of urban localized weather effects
on whole building simulation \citep{Bueno:2011hi} and urban weather generation
\citep{Bueno:2013hh}.
% Recent work in coupling geographic information systems platforms like GIS and simplified performance modeling techniques have also been completed \citep{Fonseca:2015bm}\noteDT{this is not technically a simulation coupling}.
% \subsection{Urban scale performance simulation}

@@

\subsection{Coupling process} 
The coupling process of a simplified single zone
model and contextual surrounding buildings is described in previous studies
\citep{thomas2014multiscale}, which forms the basis for the methodology
in the current effort. This process utilizes the Design Performance Viewer
(DPV) and associated workflow. The DPV is a tool written to extract and
simulate an EnergyPlus input data file (IDF) from an
Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
\citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
of the building information model from the earliest design possible that can be
used throughout the life-cycle of the building including retrofit analysis
\citep{Miller:2014tu}. This process is achieved by augmenting the information
in the BIM with default values and abstracting information not relevant for
energy simulation. The tool already has a simplified notion of surrounding
buildings, which are modeled in the BIM as simple mass objects without further
information and are exported as shading surfaces to EnergyPlus. This
functionality is used for creating the CitySim mass scene and leads to a crude
model of the urban context of the building. The current DPV philosophy of
allowing the designer to iterate rapidly on early design decisions based on
feedback about the performance of the design remains. This approach includes
streamlining the process where running a simulation requires no effort from
the designer due to automatic creation of input files, execution, and analysis
of the results.% \noteDT{not sure the second reference includes coupling...}

The coupling process of EnergyPlus and CitySim is shown in Figure
\ref{fig:OverallWorkflowProcess}. The solid lines depict the co-simulation of EnergyPlus
and CitySim and the dotted lines depict solo simulations of either EnergyPlus or CitySim. 
First, the DPV is used to extract an
EnergyPlus simulation model from the BIM. The DPV utilizes the Revit API to
extract geometrical information about the building and the physical properties
of walls, windows, doors, roofs, and floors. This information is encoded in the
BIM model as wall types, roof types, floor types as well as window and door
families. Wherever possible, the tool uses the layering and materials of the
construction types, enhancing them with physical attributes relevant to
EnergyPlus. Where not defined, it assumes default values.

@@

% On an hourly basis, CitySim performs a heating and cooling needs prediction step. The temperature determination step for the main building is replaced with the results of the EnergyPlus timestep as obtained through FMI library. The FMI library is used to send climatic and occupational data from CitySim to EnergyPlus, and to receive data from EnergyPlus that are further used within CitySim for the next time steps. 
Several key urban-scale weather variables are sent to EnergyPlus from CitySim
to account better for the localized effects of surrounding buildings,
geography and climate conditions. These variables are outlined in Table \ref{FMUimports}. 
They include various outdoor air
conditions such as dry bulb and wet bulb temperatures, dew-point, humidity, wind
speed and direction, and direct and diffuse solar radiation. These variables
overwrite the input weather variables that EnergyPlus obtains from its weather
file input. CitySim is designed to account for physical phenomenon inherent to
urban environments that are often neglected in building-scale simulation
environments \citep{Robinson:2004cr,Robinson:2009tm}. Long wave radiation
exchange between the simulated building and its surroundings is sent to
EnergyPlus; this process is described in detail in Section \ref{lwradiation}.
Finally, CitySim shares its calculated occupancy schedules as it uses a more
robust model of occupants behavior
\citep{Haldi:2011dr}.

@@

Variables sent to CitySim by EnergyPlus at each time step include several
variables related to the calculation of heating and cooling loads of a
targeted building. Table \ref{FMUexports} outlines this list of exchanged variables.
These variables are transferred due to the ability of
EnergyPlus to model more detailed building systems, schedules, ventilation and
internal load types than CitySim. For example, EnergyPlus is flexible enough
to model a detailed radiant heating and cooling system that would be
impossible in CiytSim \citep{barbara:2015tz}. EnergyPlus is an engine
optimized to accurately model building-scale systems. Thus, CitySim can take 
advantage of these models through coupling and co-simulation. EnergyPlus sends
the heating and cooling loads, the surface temperatures of the exterior
surfaces and the ventilation flow rates to CitySim.

@@

\subsection{Work flow automation}
The coupling, simulation and co-simulation process is completely managed
within a program called VisTrails \citep{Anonymous:Cayf2tu7}. The
implementation of this type of work flow is outlined in previous work focused
on automating DPV using the Kepler platform \citep{Thomas:2012wj}. This
process reduces the effort expended by a designer down to pressing a single
button. This functionality allows an iterative design style informed by
readily available simulation results. An automated work flow ties the
various steps together and maintain the effortless iterative design process.
VisTrails enables the coupling of various work flow subprocesses script
initializations, executions of the engines, and the compilation of the
outputs. This tool empowers the coupling of various executable files and their
connecting scripts in graphical diagrams that enhances reproducibility and
process automation \citep{Freire:2014tt}. The VisTrails work flow diagram for
the first case study in this paper is seen in Figure \ref{VizTrails}.

@@

\section{Implementation}\label{Implementation and results}
The co-simulation process is implemented on two case studies in Switzerland.
The first is the ETH Z\"urich Hoenggerberg campus in Z\"urich, Switzerland.
The focus of this case study is to quantify the impact of the information
exchange through co-simulation within the EnergyPlus engine. The intent on
this campus was to develop techniques for retrofit analysis using EnergyPlus.
The targeted building on this campus is the HPI Building. Raw measured data is
available for many of the buildings on campus, thus a simplified calibration
procedure is used to reconcile the simulation results.\\

The second case study is the EPFL campus in Lausanne, Switzerland. The
targeted building, in this case, was the Quartier Nord complex. The focus of
this study was to compare the solo and co-simulation output results of CitySim.
Reliable measured data for calibration is not currently available for this
building.

\subsection{Campus case study 1: ETHZ Hoenggerberg Campus}
The ETH Z\"urich Hoenggerberg campus includes 32 higher education facilities
 with spaces allocated to laboratories, office space, lecture halls,
 cafeterias, data centers and other types of similar areas. The campus has a
 centralized energy management system (EMS) that contains 807 energy and water
 measurement points from heating, cooling, electricity, city gas, domestic hot
 water, grey water, and general water consumption. %\noteDT{deleted: "buildings"}

@@

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a
CitySim model of the campus was developed. Through the workflow automation
process, this geometry was converted into an EnergyPlus input file as seen in
Figure \ref{fig:HPIcampus}. The EnergyPlus input file was then used as an input
to execute EnergyPlus solo and co-simulation processes for the purpose of
simplified calibration, and then to understand the magnitude of difference
between these simulation scenarios.

\begin{figure}[H]
\centering
\includegraphics[scale=0.2]{figures/HPI_Campus.png}
\caption{The HPI building EnergyPlus model extracted from the CitySim model. The HPI building is seen
as the light and dark brown building in the center surrounded by gray masses that represent other buildings on 
campus. The graphic is illustrated with OpenStudio for Sketch-up.}
\label{fig:HPIcampus}
\end{figure}

\subsection{Measured data collection and calibration}
Energy data from the HPI building was collected and analyzed in the context of
the simplified calibration procedures. The measured datasets were screened and
aggregated into typical usage profiles to be used for the lighting, plug-
loads, and HVAC equipment availability schedules and power densities. Figure
\ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical
energy for the HPI building. This profile was created through a filtering and
clustering process known as \emph{DayFilter} \citep{Miller:2015kr}. Cluster 0 represents
the typical energy profile for Sunday, while Cluster 1 dominates the Saturdays of the data set.
Clusters 2 and 3 make up most of the weekdays of the data set with Cluster 3 being more common in 
non-summer months. These profiles are used to set the availability schedules as inputs into the
EnergyPlus simulation to emulate the way occupants inhabit the building and
how the building management system (BMS) controls the lighting and HVAC
systems.

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/HPI_combinedclusterandcal_5}
\caption{Typical measured data electricity profiles of (left) average daily electrical consumption for each cluster and (right)
color-coded calendar of which days fall within each cluster. The diagram on the right is each month of the year with each row corresponding with
a day of the week (starting with Monday) and each column corresponding to a week of the month.}
\label{fig:hpi_elec_profiles}
\end{figure}

The measured and simulated data from both the co-simulation and EnergyPlus
solo simulation were analyzed in order to understand how both the solo and co-simulations 
compare to real, measured data. The calibration process was undertaken through a series of steps
such as including local weather conditions for the simulation period and
adding custom lighting schedules and power densities extracted from the
measured data. The models were calibrated to the summer season (May-September)
for cooling and the winter season (Jan-April and October to December) for
heating. Figure \ref{fig:hpi_measvssim} illustrates a comparison of the measured data with the
simulations after the tuning process. The final calibrated EnergyPlus solo
model had a normalized mean bias error (NMBE) of -9.36\% and a coefficient of
variation of root mean square error (CVRMSE) of 21.7\% for cooling and -9.36\%
and 29.4\% for heating. These metrics fall within the +/-10\% NMBE and +/-30\%
CVRSME used in this case study for calibration. The
goal of calibration, in this case, is to just bring the models to within a
reasonable range of reality in order to bring more confidence to analysis of
the discrepancies between the solo and co-simulation
scenarios.
